---
title: "Data prep script 1: Importing voting and post-task questionnaire data for Island Getaway Preschool Depression Study Wave T20"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
This script imports the voting and post-task questionnaire data from the Island Getaway task run in T20 wave of the PDS study.

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
```{r}
     set.seed(314)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
DISS_cleaning01_q <- read.csv("../_rawdata/ig_behavioral/IG_questionnaire.csv", na="NA")
DISS_cleaning02_q <- DISS_cleaning01_q; rm("DISS_cleaning01_q")

DISS_cleaning01_v <- read.csv("../_rawdata/ig_behavioral/IG_votes.csv", na="NA")
DISS_cleaning02_v <- DISS_cleaning01_v; rm("DISS_cleaning01_v")

save(DISS_cleaning02_q, file="./data/DISS_cleaning02_q.RData")
save(DISS_cleaning02_v, file="./data/DISS_cleaning02_v.RData")
```

# 2 Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

