---
title: "Data prep script 6: Importing cleaned ERP data from Brain Vision Analyzer to run pERP-RED analyses"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
Preprocessing of ERP/EEG data was completed in Brain Vision Analyzer. See manuscript for further details on preprocessing procedures.

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    #rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(pERPred)    #package for pERP reduction analyses
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
   Remember to set your seed AFTER you load libraries
```{r}
     set.seed(8675309)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
#Full sample
DISS_cleaned_fromBVA <- read.csv("data/DISS_cleaned_fromBVA.csv")
DISS_cleaning_pERP <- DISS_cleaned_fromBVA; rm(DISS_cleaned_fromBVA)

save(DISS_cleaning_pERP, file="./data/DISS_cleaning_pERP.RData")
```

## 2. Run pERP analyses
```{r}
# Drop unneeded columns and add Time variable
DISS_cleaning_pERP_test <- DISS_cleaning_pERP %>%
  select(-Filename) %>%
  mutate(Time=rep(seq(0,999,2),234)) %>%
  select(Subid,Condition,Time,everything()) %>%
  filter(Time>200) %>%
  arrange(Subid,Condition,Time)

DISS_cleaning_tw <- DISS_cleaning_pERP_test %>%
  group_by(Subid, Condition) %>%
  summarize(rewp = mean(FC2[between(Time,294,394)]),
            rewp275375 = mean(Cz[between(Time,275,375)]),
            rewp250350 = mean(Cz[between(Time,250,350)]),
            p2 = mean(Cz[between(Time,162,262)]),
            n2 = mean(Cz[between(Time,124,224)]))

t.test(DISS_cleaning_tw$rewp ~ DISS_cleaning_tw$Condition, paired=TRUE)
t.test(DISS_cleaning_tw$rewp275375 ~ DISS_cleaning_tw$Condition, paired=TRUE)
t.test(DISS_cleaning_tw$p2 ~ DISS_cleaning_tw$Condition, paired=TRUE)
t.test(DISS_cleaning_tw$n2 ~ DISS_cleaning_tw$Condition, paired=TRUE)


old_erp <- read.csv("/Users/brentrappaport/Box Sync/WashU/Research/DISS/_rawdata/eeg/Time_Windows/NONPCA_individual_data.csv")
old_erp_Cz <- old_erp %>%
  select(c("Subid",contains("Cz")))

DISS_cleaning_tw_comparison <- DISS_cleaning_tw %>%
  pivot_wider(id_cols=Subid, names_from=Condition, values_from=rewp250350)
corr.test(DISS_cleaning_tw_comparison$ACC, old_erp_Cz$Cz.BC_acc_250350)

DISS_cleaning_tw_comparison <- DISS_cleaning_tw %>%
  pivot_wider(id_cols=Subid, names_from=Condition, values_from=rewp275375)
corr.test(DISS_cleaning_tw_comparison$ACC, old_erp_Cz$Cz.BC_acc_275375)

# for each subject (group by), or each task, calculate the time window 296-396

# Run pERP reduction
pERPred(df=DISS_cleaning_pERP_test)
```

# 2 Save Data
```{r}
save(DISS_cleaning05, file="./data/DISS_cleaning05.RData")
```

# 3 Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

