---
title: "Data prep script 2: Cleaning voting and post-task questionnaire data for Island Getaway Preschool Depression Study Wave T20"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
This script cleans the voting and post-task questionnaire data from the Island Getaway task run in T20 wave of the PDS study. This includes calculating composite scores for the questionnaire and the proportion of votes to Keep/Kick out coplayers during the task.

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
```{r}
     set.seed(314)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
      base::load(file = "./data/DISS_cleaning02_q.RData")   
      DISS_cleaning03_q <- DISS_cleaning02_q  ## first create new data
      rm("DISS_cleaning02_q")             ## remove old data
      
      base::load(file = "./data/DISS_cleaning02_v.RData")   
      DISS_cleaning03_v <- DISS_cleaning02_v  ## first create new data
      rm("DISS_cleaning02_v")             ## remove old data
```

## 1.6 Aggregate post-task questionnaire responses
```{r}
DISS_cleaning03_q$r <- as.integer(DISS_cleaning03_q$r) #make into an integer
DISS_cleaning03_q <- DISS_cleaning03_q %>%
  mutate(r_temp  = ifelse(qn<3, 6-r, r)) %>% #reverse score appropriate items
  mutate(r_new = ifelse(subscale=="self-esteem", ifelse(qn==3, 6-r, r_temp), r_temp)) #fix self-esteem scale (since question number 4 is actually reverse coded, so instead for parsimony we recode it as poor self-esteem and reverse code questions 1-3 instead)

DISS_cleaning03_q$subscale <- dplyr::recode(DISS_cleaning03_q$subscale, "self-esteem"="poor_self_esteem")

tapply(DISS_cleaning03_q$r_new, DISS_cleaning03_q$subscale, function(x) c(mean(x, na.rm=T), sd(x, na.rm=T))) #get the mean and sd for each dimension in the questionnaire

DISS_cleaning03_q <- as.data.frame(t(tapply(DISS_cleaning03_q$r_new, DISS_cleaning03_q[,c("subscale","s")], function(x) mean(x, na.rm=T))))
DISS_cleaning03_q$Subid <- as.integer(row.names(DISS_cleaning03_q))
names(DISS_cleaning03_q) <- gsub(" ", "_", names(DISS_cleaning03_q))
names(DISS_cleaning03_q) <- gsub("-", "_", names(DISS_cleaning03_q))
```

## 1.7 Generate column of coplayer votes
```{r}
# 0 is Kick, 1 is Keep

DISS_cleaning04_v <- DISS_cleaning03_v %>%
  mutate(coplayer_priorvote = 
           case_when(round == 2 & grepl('xpendable_a',coplayer) ~ "Keep",
                     round == 3 & grepl('xpendable_a',coplayer) ~ "Kick",
                     round == 4 & grepl('xpendable_a',coplayer) ~ "Keep",
                     round == 5 & grepl('xpendable_a',coplayer) ~ "Kick",
                     round == 6 & grepl('xpendable_a',coplayer) ~ "Keep",
                     
                     round == 2 & grepl('xpendable_r',coplayer) ~ "Kick",
                     round == 3 & grepl('xpendable_r',coplayer) ~ "Keep",
                     round == 4 & grepl('xpendable_r',coplayer) ~ "Kick",
                     round == 5 & grepl('xpendable_r',coplayer) ~ "Keep",
                     round == 6 & grepl('xpendable_r',coplayer) ~ "Kick",
                     
                     round == 2 & coplayer=='a1' ~ "Kick",
                     round == 3 & coplayer=='a1' ~ "Kick",
                     round == 4 & coplayer=='a1' ~ "Kick",
                     round == 5 & coplayer=='a1' ~ "Keep",
                     round == 6 & coplayer=='a1' ~ "Kick",
                     
                     round == 2 & coplayer=='a2' ~ "Keep",
                     round == 3 & coplayer=='a2' ~ "Kick",
                     round == 4 & coplayer=='a2' ~ "Keep",
                     round == 5 & coplayer=='a2' ~ "Kick",
                     round == 6 & coplayer=='a2' ~ "Kick",
                     
                     round == 2 & coplayer=='a3' ~ "Kick",
                     round == 3 & coplayer=='a3' ~ "Keep",
                     round == 4 & coplayer=='a3' ~ "Keep",
                     round == 5 & coplayer=='a3' ~ "Kick",
                     round == 6 & coplayer=='a3' ~ "Kick",
                     
                     round == 2 & coplayer=='a4' ~ "Keep",
                     round == 3 & coplayer=='a4' ~ "Kick",
                     round == 4 & coplayer=='a4' ~ "Kick",
                     round == 5 & coplayer=='a4' ~ "Keep",
                     round == 6 & coplayer=='a4' ~ "Keep",
                     
                     round == 2 & coplayer=='a5' ~ "Keep",
                     round == 3 & coplayer=='a5' ~ "Keep",
                     round == 4 & coplayer=='a5' ~ "Kick",
                     round == 5 & coplayer=='a5' ~ "Keep",
                     round == 6 & coplayer=='a5' ~ "Keep"
                     ))
```

## 1.8 Aggregate voting responses (Keep/Stay, Kick out)
```{r}
DISS_cleaning04_v$Subid <- as.integer(DISS_cleaning04_v$s)
DISS_cleaning04_v2 <- DISS_cleaning04_v %>%
  group_by(Subid) %>%
  count(vote=="Kick") %>%
  spread(`vote == "Kick"`, n) %>%
  rename(Kick = "TRUE",
         Keep = "FALSE") %>%
  mutate(Keep_prop = Keep/51,
         Kick_prop = Kick/51)

# Calculate the proportion of Keep votes cast when that coplayer had voted to keep the subject in the prior round (suggested by Autumn)
DISS_cleaning04_v3 <- DISS_cleaning04_v %>%
  filter(coplayer_priorvote == "Keep") %>%
  group_by(Subid) %>%
  count(vote=="Kick") %>%
  spread(`vote == "Kick"`, n) %>%
  rename(Kick = "TRUE",
         Keep = "FALSE") %>%
  mutate(Keep_prop_pr = Keep/51) %>%
  select(Subid,Keep_prop_pr)

DISS_cleaning04_vq <- Reduce(function(x,y) merge(x,y,by="Subid",all=FALSE), list(DISS_cleaning03_q, DISS_cleaning04_v2, DISS_cleaning04_v3)) #merge the two datasets
```

# 2 Save data
```{r}
save(DISS_cleaning04_vq, file="./data/DISS_cleaning04_vq.RData")
```

# 3 Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

