---
title: "Data prep script 3: Pulling needed symptom and demographic variables"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
This script imports the CRUNCH dataset and selects only the symptom and demographic variables to be used in further analyses.

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    #rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  # renv::restore()     #restore environment
renv::restore()

  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
```{r}
     set.seed(8675309)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
CRUNCH <- expss::read_spss("../../CRUNCH/PDS_III_S5_crunched_08_28_20.sav")
crunch <- CRUNCH; rm(CRUNCH)
```

# 2. Calculate variables
## 2.1. Remove subjects with IQ <70
```{r}
crunch$Subid <- as.integer(as.character(crunch$Subid))
crunch <- crunch %>%
  dplyr::filter(IQ>=70 | is.na(IQ))
```

## 2.2. If missing S5Income_to_Need pull from earlier waves
```{r}
crunch$Income_to_Need <- ifelse(is.na(crunch$S5Income_to_Need), crunch$S4Income_to_Need, crunch$S5Income_to_Need)
crunch$Income_to_Need <- ifelse(is.na(crunch$Income_to_Need), crunch$S3Income_to_Need, crunch$Income_to_Need)
crunch$Income_to_Need <- ifelse(is.na(crunch$Income_to_Need), crunch$S2Income_to_Need, crunch$Income_to_Need)
crunch$Income_to_Need <- ifelse(is.na(crunch$Income_to_Need), crunch$S1Income_to_Need, crunch$Income_to_Need)
```

## 2.3. Remove unneeded variables
```{r}
demog <- c("Subid","sex","T20age","ethin","PDSIII_Race","PDSIII_Race_other","PDSIII_Hispanic",
           "Income_to_Need",
           "S5psychmed","S5psychmed_dos")
symptoms <- c("S5CDI2C_T","S5CDI2C_TT","S5CDI2P_T","S5CDI2P_TT","S5BDItotalscore",
              "S5SIAS6_score","S5SPS6_score")

DISS_cleaning04_crunch <- crunch %>%
  dplyr::select(demog,symptoms,
                matches('MDD|SOC'))
```

## Detect missing data
```{r}
DISS_cleaning04_crunch[!complete.cases(DISS_cleaning04_crunch$S5BDItotalscore),]

DISS_cleaning04_crunch %>%
     rowid_to_column() %>%
     filter(is.na(S5BDItotalscore))

sapply(DISS_cleaning04_crunch[,c], function(x) sum(is.na(x)))

DISS_cleaning04_crunch %>%
  filter(is.na(S5BDItotalscore) & is.na(S5CDI2C_T))
mydata %>% 
  filter(! is.na(important_a) | ! is.na(important_b))

DISS_cleaning04_crunch[DISS_cleaning04_crunch$Subid,is.na(DISS_cleaning04_crunch$S5BDItotalscore) & is.na(DISS_cleaning04_crunch$S5CDI2C_T)]
```

## 2.4. Combine CDI/BDI and SIAS/SPS
```{r}
# Combine CDI and BDI
DISS_cleaning04_crunch$S5bdi_perc <- (DISS_cleaning04_crunch$S5BDItotalscore/63)*100
DISS_cleaning04_crunch$S5cdic_perc <- (DISS_cleaning04_crunch$S5CDI2C_T/56)*100
DISS_cleaning04_crunch$S5cdic_bdi_perc <- DISS_cleaning04_crunch$S5cdic_perc
DISS_cleaning04_crunch$S5cdic_bdi_perc[!is.na(DISS_cleaning04_crunch$S5bdi_perc)] <- DISS_cleaning04_crunch$S5bdi_perc[!is.na(DISS_cleaning04_crunch$S5bdi_perc)] 

# Average SIAS-6 and SPS-6 together
DISS_cleaning04_crunch$S5_SIASSPS <- rowMeans(DISS_cleaning04_crunch[,c("S5SIAS6_score","S5SPS6_score")])
```

# 3. Save new data
```{r}
save(DISS_cleaning04_crunch, file="./data/DISS_cleaning04_crunch.RData")
```

# 4. Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

