---
title: "Data prep script 8: Conducting multiple imputation (MI) of data"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
These are the primary analyses for Brent Rappaport's doctoral dissertation thesis: "Behavioral, neural, and psychiatric correlates of response to social feedback."

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    options(scipen = 999) #Disable scientific notation
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(MASS)       #runs robust linear models
  library(sfsmisc)    #run robust F-test for linear models
  library(MissMech)   #test of MCAR
#To install from archive: install.packages("https://cran.r-project.org/src/contrib/Archive/MissMech/MissMech_1.0.2.tar.gz", repos=NULL, type="source")
  library(naniar)     #handle missingness
  library(mice)       #multiple imputation
  library(miceadds)   #adding functions to mice
  library(tidyverse)  #plotting/cleaning, etc.
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
   Remember to set your seed AFTER you load libraries
```{r}
     set.seed(314)    #Set seed
```

## 1.5. Load data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
      load(file = "./data/DISS_cleaning07.RData")   
      DISS_do01_full <- DISS_cleaning07  ## first create new data
      rm("DISS_cleaning07")             ## remove old data
```      

## 1.6. Subset data
```{r}
# List of variables to include in subsetted data
all_measures_list <- c("rewp_r","fn_r",
                       "Reward_bias_20","Loss_bias_20",
                       "S5cdic_bdi_perc","S5_SIASSPS",
                       "T20age","Income_to_Need","sex_f","PDSIII_Race_f","PDSIII_Hispanic_f",
                       "p2_r","n1_r","T20_MDD","T20_SOC",
                       "PILTP_Disc_20","PILTN_Disc_20",
                       "S5BAS_C_drive","S5BAS_C_funseek2","S5BAS_C_reward_revised2","S5BIS_C_revised","S5PSCtotal",
                       "S5ListSort_AgeAdjustedSS","S5PatComp_AgeAdjustedSS","S5PictSeq_AgeAdjustedSS","S5PictVocab_AgeAdjustedSS","S5Flanker_AgeAdjustedSS")
all_measures_list_n <- c("rewp_r","fn_r",
                       "Reward_bias_20","Loss_bias_20",
                       "S5cdic_bdi_perc","S5_SIASSPS",
                       "T20age","Income_to_Need","sex","PDSIII_Race","PDSIII_Hispanic",
                       "p2_r","n1_r","T20_MDD","T20_SOC",
                       "PILTP_Disc_20","PILTN_Disc_20",
                       "S5BAS_C_drive","S5BAS_C_funseek2","S5BAS_C_reward_revised2","S5BIS_C_revised","S5PSCtotal",
                       "S5ListSort_AgeAdjustedSS","S5PatComp_AgeAdjustedSS","S5PictSeq_AgeAdjustedSS","S5PictVocab_AgeAdjustedSS","S5Flanker_AgeAdjustedSS")

# Measures of interest
measures_list <- c("rewp_r","fn_r","p2_r","n1_r","Reward_bias_20","Loss_bias_20","S5cdic_bdi_perc","S5_SIASSPS","T20age","Income_to_Need")

# Make lists to be used below
var_interest_n <- c("rewp_r","fn_r","Reward_bias_20","Loss_bias_20","S5cdic_bdi_perc","S5_SIASSPS","T20age","Income_to_Need","sex","PDSIII_Race","PDSIII_Hispanic","S5psychmed_dos")
var_interest_f <- c("rewp_r","fn_r","Reward_bias_20","Loss_bias_20","S5cdic_bdi_perc","S5_SIASSPS","T20age","Income_to_Need","sex_f","PDSIII_Race_f","PDSIII_Hispanic_f","S5psychmed_dos_f")
var_interest_nocovar <- c("rewp_r","fn_r","Reward_bias_20","Loss_bias_20","S5cdic_bdi_perc","S5_SIASSPS")
```

# 2. Factors
```{r}
# Make appropriate covariates factors
factors_list <- c("sex","PDSIII_Race","PDSIII_Hispanic","S5psychmed_dos")
for (f in factors_list){ eval(parse(text=paste0("DISS_do01_full$",f,"_f <- with(DISS_do01_full, as.factor(",f,"))"))) }

# Dummy code all factors
contrasts(DISS_do01_full$sex_f) <- contr.treatment(2); contrasts(DISS_do01_full$PDSIII_Race_f) <- contr.treatment(3); contrasts(DISS_do01_full$PDSIII_Hispanic_f) <- contr.treatment(2); contrasts(DISS_do01_full$S5psychmed_dos_f) <- contr.treatment(2)
```

# 3. Subset data
```{r}
# Subset data to only include those that completed Island Getaway task and have T20age, and only include variables to be used in multiple imputation
DISS_do01 <- DISS_do01_full %>%
    drop_na(rewp_r, T20age) %>%
    dplyr::select(c(Subid, all_of(all_measures_list), all_of(factors_list), paste0(factors_list,"_f")))
```

# 3. Check for univariate & multivariate outliers (not including covariates)
Do NOT include covariates, otherwise this leads to excuding the 3 Hispanic subjects
```{r Outliers}
# Inspect for univariate outliers
apply(DISS_do01[,var_interest_f[1:6]], 2, function(x) which(x > (mean(x, na.rm=T)+3*sd(x, na.rm=T)) | x < (mean(x, na.rm=T)-3*sd(x, na.rm=T))))

# Identify multivariate outliers
data_p <- psych::outlier(DISS_do01[,var_interest_nocovar],plot = T,bad=10,na.rm=T)
rows_to_exclude <- which(pchisq(data_p,df=6,ncp=0,lower.tail = F,log.p = F)<.001)
paste0("Outlier Subid: ",rows_to_exclude)

# Pare down dataset
DISS_do01_full_outliers <- DISS_do01_full %>%
  drop_na(rewp_r, T20age)

# Remove multivariate outliers
## For full dataset
DISS_do01_full_nooutliers <- DISS_do01_full %>%
    drop_na(rewp_r, T20age) %>%
    dplyr::slice(-rows_to_exclude)
## For subsetted dataset
DISS_do01_nooutliers <- DISS_do01 %>%
    dplyr::slice(-rows_to_exclude)

# Check that both datasets removed same number of participants
length(DISS_do01_full_nooutliers$Subid); length(DISS_do01_nooutliers$Subid)
```
2 removed as multivariate outlier (as of 03/29/21)

# 4. Missing data
```{r}
sum(complete.cases(DISS_do01_nooutliers$rewp_r)) #number of participants that completed IG with good data

DISS_do01_nooutliers %>% #missing data for each variable
  dplyr::select(c(measures_list,paste0(factors_list[1:3],"_f"))) %>%
  miss_var_summary(order=FALSE)
```

## 4.1. Test MCAR
```{r}
TestMCARNormality(data=DISS_do01_nooutliers[,c(var_interest_n)], imputation.number=10, imputation.method="Dist.Free", seed=314, del.lesscases=2)

# TestMCARNormality(data=DISS_do01_nooutliers[,all_measures_list_n], imputation.number=10, imputation.method="Dist.Free", seed=314)
```
The non-parametric test shows that there is not sufficient evidence to rejection MCAR asssumption, therefore data are assumed to be missing completely at random.

"So the results of the test of MCAR for homogenity of covariances show us, that mcar was not rejected because of non-normality or heteroscedasticity. If the Hawkins-test becomes significant, the „MissMech“-package performs a nonparametric test on homoscedasticity. This way, it can show through the method of elimination if non-normality or heteroscedasticity is a problem." (https://statistics.ohlsen-web.de/multiple-imputation-with-mice/)

## 4.2. Multiple imputation
Conduct multiple imputation using package 'mice' and the following steps outlined here: 
http://dept.stat.lsa.umich.edu/~jerrick/courses/stat701/notes/mi.html
```{r}
md.pattern(DISS_do01_nooutliers[,var_interest_f])
md.pattern(DISS_do01_nooutliers[,all_measures_list])

MI_data <- DISS_do01_nooutliers[,c(all_measures_list, "S5psychmed_dos_f")]
m0 <- mice(MI_data, maxit=0)
meth <- m0$method
meth[names(meth) %in% c("S5psychmed_dos_f")] <- ""
pred <- m0$predictorMatrix
pred[, colnames(pred) %in% c("S5psychmed_dos_f")] <- 0
DISS_do01.imp <- mice(MI_data, predictorMatrix=pred, method=meth, m=10, seed=314)

summary(DISS_do01.imp)

DISS_do01.comp <- complete(DISS_do01.imp, "long", include = TRUE)
```

## 4.2.1. Check imputed values (line indicates mean)
```{r}
DISS_do01.comp$Reward_bias_20.NA <- cci(DISS_do01_nooutliers$Reward_bias_20)
DISS_do01.comp$Loss_bias_20.NA <- cci(DISS_do01_nooutliers$Loss_bias_20)
DISS_do01.comp$S5cdic_bdi_perc.NA <- cci(DISS_do01_nooutliers$S5cdic_bdi_perc)
DISS_do01.comp$S5psychmed_dos_f.NA <- cci(DISS_do01_nooutliers$S5psychmed_dos_f)

# Reward bias
ggplot(DISS_do01.comp, aes(x = .imp, y = Reward_bias_20)) + 
  geom_jitter(aes(color=Reward_bias_20.NA), show.legend = FALSE, width = .2) +
  geom_line(stat="summary", show.legend = FALSE)

# Loss avoidance
ggplot(DISS_do01.comp, aes(x = .imp, y = Loss_bias_20)) + 
  geom_jitter(aes(color=Loss_bias_20.NA), show.legend = FALSE, width = .2) +
  geom_line(stat="summary", show.legend = FALSE)

# Current depression severity
ggplot(DISS_do01.comp, aes(x = .imp, y = S5cdic_bdi_perc)) + 
  geom_jitter(aes(color=S5cdic_bdi_perc.NA), show.legend = FALSE, width = .2) +
  geom_line(stat="summary", show.legend = FALSE)

# S5 psychotropic med use (should be no imputed values)
ggplot(DISS_do01.comp, aes(x = .imp, y = S5psychmed_dos_f)) + 
  geom_jitter(aes(color=S5psychmed_dos_f.NA), show.legend = FALSE, width = .2) +
  geom_line(stat="summary", show.legend = FALSE)
```

# 6. Standardize measures
Center and standardize all measures to make b estimates from multiple regressions more interpretable.
```{r}
#convert into datlist
DISS_do01.dat <- miceadds::mids2datlist(DISS_do01.imp)
#scale/standardize datlist
DISS_do01.dat_z <- scale_datlist(datlist=DISS_do01.dat, orig_var=measures_list, trafo_var=paste0(measures_list,"_z"), weights=NULL, M=0, SD=1, digits=NULL)
#convert back to mids
DISS_do01.imp_z <- miceadds::datlist2mids(DISS_do01.dat_z)

#standardize measures in non-imputed dataset
for (m in measures_list){
 eval(parse(text=paste0("DISS_do01$",m,"_z <- scale(DISS_do01$",m,", center=T, scale=T)")))
}

for (m in measures_list){
 eval(parse(text=paste0("DISS_do01_nooutliers$",m,"_z <- scale(DISS_do01_nooutliers$",m,", center=T, scale=T)")))
}
```

# 7. Save data
```{r}
#save non-imputed full dataset w/ outliers
save(DISS_do01_full_outliers, file="./data/DISS_do01_full_outliers.RData")
#save non-imputed dataset w/ outliers
save(DISS_do01, file="./data/DISS_do01.RData")
#save non-imputed full dataset wo/ outliers
save(DISS_do01_full_nooutliers, file="./data/DISS_do01_full.RData")
#save non-imputed dataset wo/ outliers
save(DISS_do01_nooutliers, file="./data/DISS_do01_nooutliers.RData")
#save imputed dataset(s)
save(DISS_do01.imp, file="./data/DISS_do01.imp.RData")
#save standardized imputed dataset(s)
save(DISS_do01.imp_z, file="./data/DISS_do01.imp_z.RData")
```

# 8. Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

