---
title: "Data prep script 1: Importing and merging self-report data"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
This script imports and merges the self-report data from BUDS study: Bullying, Unsupportive family/peers, Discrimination, and Social feedback study using data from PREDICT project collaboration between Northwestern (Shankman) and Columbia (Auerbach).

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
```{r}
     set.seed(312)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
# Import data from Columbia University
BUDS_cleaning01_columbia <- read.csv("../_rawdata/SP_Self-Report_Baseline (3.17.21)_August 1, 2022_14.08.csv")
BUDS_cleaning02_columbia <- BUDS_cleaning01_columbia; rm("BUDS_cleaning01_columbia")

# Import data from Northwestern University
BUDS_cleaning01_nw <- read.csv("../_rawdata/SP_Self-Report_Baseline (3.17.21)_August 1, 2022_14.08.csv")
BUDS_cleaning02_nw <- BUDS_cleaning01_nw; rm("BUDS_cleaning01_nw")
```

```{r}
DISS_cleaning07 <- Reduce(function(x,y) merge(x,y,by="id_1_i",all=TRUE),list(BUDS_cleaning02_columbia, BUDS_cleaning02_nw))
```

```{r}
save(BUDS_cleaning02, file="data/BUDS_cleaning02.RData")
```

# 2 Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

