---
title: "Data prep script 4: Pulling needed HBQ variables"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
This script imports and cleans data from the MacArthur Health & Behavior Questionnaire to measure peer relations in the PDS sample. This is primarily or the analyses found in 'do_supplement.Rmd' which are a follow-up to Rappaport et al., 2019.

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  # renv::restore()     #restore environment
renv::restore()

  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
```{r}
     set.seed(314)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
# Load HBQ
data_hbq <- read.csv("../../CRUNCH/-HBQ/HBQ_dataset.csv")
# data_hbq_t1 <- expss::read_spss("../../CRUNCH/-HBQ/R01 Val PDS T1 HBQ-P CL_BT (10 24 16).sav")
# data_hbq_t3 <- expss::read_spss("../../CRUNCH/-HBQ/R01 Val PDS T3 HBQ-P CL_BT (10 24 16).sav")
# data_hbq_t5 <- expss::read_spss("../../CRUNCH/-HBQ/R01 Val PDS T5 HBQ-P CL_BT (10 24 16).sav")
# data_hbq_t6 <- expss::read_spss("../../CRUNCH/-HBQ/R01 Val PDS T6 HBQ-P CL_BT (10 24 16).sav")
# data_hbq_t8 <- expss::read_spss("../../CRUNCH/-HBQ/R01 Val PDS T8 HBQ-P CL_BT (10 24 16).sav")
# data_hbq_t10 <- expss::read_spss("../../CRUNCH/-HBQ/R01 Val PDS T10 HBQ-P CL_BT (10 24 16).sav")
# data_hbq_t12 <- expss::read_spss("../../CRUNCH/-HBQ/R01 Val PDS T12 HBQ-P CL_BT (10 24 16).sav")
# data_hbq_t14 <- expss::read_spss("../../CRUNCH/-HBQ/R01 Val PDS T14 HBQ-P CL_BT (10 24 16).sav")
# data_hbq_t18 <- expss::read_spss("../../CRUNCH/-HBQ/R01 PDS-III Imaging T18 HBQ-P (9 7 17).sav")

data_hbq$Subid <- as.integer(data_hbq$Subid)

data_hbq_t1$Subid <- as.integer(data_hbq_t1$Subid)
data_hbq_t3$Subid <- as.integer(data_hbq_t3$Subid)
data_hbq_t5$Subid <- as.integer(data_hbq_t5$Subid)
data_hbq_t7$Subid <- as.integer(data_hbq_t6$Subid)
data_hbq_t8$Subid <- as.integer(data_hbq_t8$Subid)
data_hbq_t10$Subid <- as.integer(data_hbq_t10$Subid)
data_hbq_t12$Subid <- as.integer(data_hbq_t12$Subid)
data_hbq_t14$Subid <- as.integer(data_hbq_t14$Subid)
data_hbq_t18$Subid <- as.integer(data_hbq_t18$Subid)

for (m in c(1,3,5,6,8,10,12,14,18)) {
  eval(parse(text=paste0("data_hbq_t",m,"$Subid <- as.integer(data_hbq_t",m,"$Subid)")))
}

DISS_cleaning04_hbq <- data_hbq

DISS_cleaning04_hbq <- Reduce(function(x,y) merge(x,y,by="Subid",all=TRUE),list(data_hbq_t1,data_hbq_t3,data_hbq_t5,data_hbq_t18))
rm(data_hbq_t1,data_hbq_t3,data_hbq_t5,data_hbq_t18)
```

```{r}
DISS_cleaning04_hbq$T6hbqPR <- DISS_cleaning04_hbq$T6hbqhPR
DISS_cleaning04_hbq$T6hbqPR[!is.na(DISS_cleaning04_hbq$T6hbqpPR)] <- DISS_cleaning04_hbq$T6hbqpPR[!is.na(DISS_cleaning04_hbq$T6hbqpPR)] 

DISS_cleaning04_hbq$T8hbqPR <- DISS_cleaning04_hbq$T8hbqhPR
DISS_cleaning04_hbq$T8hbqPR[!is.na(DISS_cleaning04_hbq$T8hbqpPR)] <- DISS_cleaning04_hbq$T8hbqpPR[!is.na(DISS_cleaning04_hbq$T8hbqpPR)] 
```

## 1.6 Remove unneeded variables
```{r}
# hbq_measures <- c("T1hbqpPR","T3hbqpPR","T5hbqpPR","T18hbqhPR")

# DISS_cleaning04_hbq <- DISS_cleaning04_hbq %>%
  # dplyr::select("Subid",hbq_measures)
```

## 1.7 Reverse score HBQ scales
```{r}
for (m in c(1,3,5)) { 
  eval(parse(text=paste0("DISS_cleaning04_hbq$T",m,"hbqpPRr <- 5-DISS_cleaning04_hbq$T",m,"hbqpPR"))) 
  }
DISS_cleaning04_hbq$T18hbqhPRr <- 5-DISS_cleaning04_hbq$T18hbqhPR
```

## 1.8 Calculate early peer victimization score
```{r}
# Calculate early peer victimization score
DISS_cleaning04_hbq$PPr_Avg_early <- ifelse(!is.na(DISS_cleaning04_hbq$T1hbqpPRr | 
                                                   DISS_cleaning04_hbq$T3hbqpPRr | 
                                                   DISS_cleaning04_hbq$T5hbqpPRr),
                        rowMeans(DISS_cleaning04_hbq[,c("T1hbqpPRr","T3hbqpPRr","T5hbqpPRr")], na.rm=T),NA)
```

# 2 Save new data
```{r}
save(DISS_cleaning04_hbq, file="./data/DISS_cleaning04_hbq.RData")
```

# 3 Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

