---
title: "Data prep script 6: Create time windows from PCA analyses"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
Preprocessing of ERP/EEG data was completed in Brain Vision Analyzer and time windows are based on peak latency extracted from EP Toolkit. See manuscript for further details on preprocessing procedures.

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    options(scipen = 999) #Disable scientific notation
    #rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(MASS)       #to residualize ERP scores with stdres
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(pERPred)    #package for pERP reduction analyses
  library(tidyverse)  #plotting/cleaning, etc.
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
   Remember to set your seed AFTER you load libraries
```{r}
     set.seed(8675309)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
#Full sample
DISS_cleaned_fromBVA <- read.csv("../_rawdata/DISS_cleaned_fromBVA.csv")
DISS_cleaning06_pca <- DISS_cleaned_fromBVA; rm(DISS_cleaned_fromBVA)

save(DISS_cleaning06_pca, file="./data/DISS_cleaning06_pca.RData")
```

# 2. Create subject level component averages
```{r}
# Drop unneeded columns and add Time variable
DISS_cleaning_tw_time <- DISS_cleaning06_pca %>%
  dplyr::select(-Filename) %>%
  mutate(Time=rep(seq(-200,799,2),234)) %>%
  dplyr::select(Subid,Condition,Time,everything()) %>%
  filter(Time>0) %>%
  arrange(Subid,Condition,Time)

DISS_cleaning_tw_components <- DISS_cleaning_tw_time %>%
  group_by(Subid, Condition) %>%
  summarize(rewp = mean(FC2[between(Time,294,394)]),
            rewp275375 = mean(Cz[between(Time,275,375)]),
            rewp250350 = mean(Cz[between(Time,250,350)]),
            p2 = mean(Cz[between(Time,162,262)]),
            n2 = mean(Cz[between(Time,124,224)]))
```

## 2.1 Check differences between conditions using t-test
```{r}
rewp_ttest <- t.test(DISS_cleaning_tw_components$rewp ~ DISS_cleaning_tw_components$Condition, paired=TRUE)[1:3]
p2_ttest <- t.test(DISS_cleaning_tw_components$p2 ~ DISS_cleaning_tw_components$Condition, paired=TRUE)[1:3]
n2_ttest <- t.test(DISS_cleaning_tw_components$n2 ~ DISS_cleaning_tw_components$Condition, paired=TRUE)[1:3]

#Apply FDR correction
p.adjust(c(rewp_ttest[3],p2_ttest[3],n2_ttest[3]), "fdr")
```

# 3. Create residualized scores
```{r}
#Make data into wide format
DISS_cleaning_tw_components_wide <- DISS_cleaning_tw_components %>%
  pivot_wider(id_cols=Subid, names_from=Condition, values_from=c(rewp,rewp275375,rewp250350,p2,n2))

component_list <- c("rewp","rewp275375","rewp250350","p2","n2")

for (c in component_list){ 
    eval(parse(text=paste0("DISS_cleaning_tw_components_wide$",c,"_r <- stdres(lm(",c,"_ACC ~ ",c,"_REJ, DISS_cleaning_tw_components_wide, na.action=na.exclude))"))) 
}

DISS_cleaning_tw_components_wide$fn_r <- stdres(lm(rewp_REJ ~ rewp_ACC, DISS_cleaning_tw_components_wide, na.action=na.exclude))
DISS_cleaning06_tw <- DISS_cleaning_tw_components_wide
```

# 3. Save Data
```{r}
save(DISS_cleaning06_tw, file="./data/DISS_cleaning06_tw.RData")
```

# 4. Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

