---
title: "Data prep script 7: Merging all data together"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    options(scipen = 999) #Disable scientific notation
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
   Remember to set your seed AFTER you load libraries
```{r}
     set.seed(314)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
      # Voting behavior and post-task questionnaire responses
      load(file = "./data/DISS_cleaning03_vq.RData")   
      DISS_cleaning07_beh <- DISS_cleaning03_vq  ## first create new data
      rm("DISS_cleaning03_vq")             ## remove old data
      
      # Symptom measures
      load(file = "./data/DISS_cleaning04_crunch.RData")   
      DISS_cleaning07_crunch <- DISS_cleaning04_crunch  ## first create new data
      rm("DISS_cleaning04_crunch")             ## remove old data
      
      # Peer relations measures
      load(file = "./data/DISS_cleaning04_hbq.RData")   
      DISS_cleaning07_hbq <- DISS_cleaning04_hbq  ## first create new data
      rm("DISS_cleaning04_hbq")             ## remove old data
      
      # Reward/loss behavioral task (PILT)
      load(file = "./data/DISS_cleaning05_pilt.RData")   
      DISS_cleaning07_pilt <- DISS_cleaning05_pilt  ## first create new data
      rm("DISS_cleaning05_pilt")             ## remove old data
      
      # ERP PCA component values
      load(file = "./data/DISS_cleaning06_tw.RData")   
      DISS_cleaning07_tw <- DISS_cleaning06_tw  ## first create new data
      rm("DISS_cleaning06_tw")             ## remove old data
      
```

## 1.6 Merge Behavioral data with CRUNCH
```{r}
DISS_cleaning07 <- Reduce(function(x,y) merge(x,y,by="Subid",all=TRUE),list(DISS_cleaning07_crunch, DISS_cleaning07_hbq, DISS_cleaning07_beh, DISS_cleaning07_pilt, DISS_cleaning07_tw))
```

# 2 Save Data
```{r}
save(DISS_cleaning07, file="./data/DISS_cleaning07.RData")
```

# 3 Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

