---
title: "Analysis script 2: Frequentist analysis of confirmatory analyses"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
These are the primary analyses for Brent Rappaport's doctoral dissertation thesis: "Behavioral, neural, and psychiatric correlates of response to social feedback."

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    options(scipen = 999) #Disable scientific notation
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(mice)       #multiple imputation
  library(miceadds)   #adding functions to mice
  library(tidyverse)  #plotting/cleaning, etc.
  library(pander)     #make nice tables
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
   Remember to set your seed AFTER you load libraries
```{r}
     set.seed(919)    #Set seed
```

## 1.5. Load data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
      load(file = "./data/DISS_do01.RData")   
      DISS_do02 <- DISS_do01  ## first create new data
      rm("DISS_do01")             ## remove old data
      
      load(file = "./data/DISS_do01.imp_z.RData")
      DISS_do02.imp_z <- DISS_do01.imp_z
      rm("DISS_do01.imp_z")
```      

## 1.6. Function to write tables
```{r}
DISS_make_table <- function(first_model, second_model) {
  table_x <- as.data.frame(matrix(nrow=9, ncol=7))
  colnames(table_x) <- c("Predictor", "b","95%_CI", "p", "b","95%_CI", "p")
  table_x[,1] <- as.character(summary(first_model)$term)
  table_x[,2] <- round(summary(first_model)$est,3)
  table_x[,3] <- paste0(round(summary(first_model, conf.int=TRUE, conf.level = 0.95)[,7],3),
                         ", ",round(summary(first_model, conf.int=TRUE, conf.level = 0.95)[,8],3))
  table_x[,4] <- round(summary(first_model)$p,3)
  table_x[,5] <- round(summary(second_model)$est,3)
  table_x[,6] <- paste0(round(summary(second_model, conf.int=TRUE, conf.level = 0.95)[,7],3),
                         ", ",round(summary(second_model, conf.int=TRUE, conf.level = 0.95)[,8],3))
  table_x[,7] <- round(summary(second_model)$p,3)
  return(table_x)
}
```

# 2. Primary confirmatory analyses
### 2.1. Zero-order correlations
```{r}
zero_order_cor <- micombine.cor(DISS_do02.imp_z, variables=c("rewp_r_z","fn_r_z",
                                          "Reward_bias_20_z","Loss_bias_20_z",
                                          "S5cdic_bdi_perc_z","S5_SIASSPS_z"), 
              conf.level=0.95, method="pearson", nested=FALSE, partial=NULL) %>%
  mutate_if(is.numeric, round, 3)

zero_order_cor_star <- zero_order_cor %>%
  mutate(r_new=case_when(p<.01~paste0(r,"**"), p<.05~paste0(r,"*"), TRUE~paste0(r))) %>%
  select(variable1,variable2,r_new,p,r)

zero_order_r <- round(attr(zero_order_cor, "r_matrix"),3)
zero_order_rse <- round(attr(zero_order_cor, "rse_matrix"),3)

zero_order_matrix <- matrix(NA, nrow=6, ncol=6)
zero_order_matrix[upper.tri(zero_order_matrix)] <- zero_order_r[upper.tri(zero_order_r)]
zero_order_matrix[lower.tri(zero_order_matrix)] <- zero_order_rse[lower.tri(zero_order_rse)]
row.names(zero_order_matrix) <- c("RewP","FN","Reward Bias","Loss Avoidance", "Depression", "Social Anxiety")
colnames(zero_order_matrix) <- c("RewP","FN","Reward Bias","Loss Avoidance", "Depression", "Social Anxiety")
zero_order_matrix
write.csv(x=as.data.frame(zero_order_matrix), file="./tables/Correlations.csv", row.names=TRUE)
```
The upper diagonal is the r's, the lower diagonal is the rse's.

## 2.2. Aim 1: Relationship between RewP/FN and PILT-P/N
```{r}
mr.rewp_pilt <- pool(with(data=DISS_do02.imp_z, expr=lm(rewp_r_z ~ Reward_bias_20_z + Loss_bias_20_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z)))
summary(pool(with(data=DISS_do02.imp_z, expr=lm(rewp_r_z ~ Reward_bias_20_z + Loss_bias_20_z))))

mr.fn_pilt <- pool(with(data=DISS_do02.imp_z, expr=lm(fn_r_z ~ Reward_bias_20_z + Loss_bias_20_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z)))
summary(pool(with(data=DISS_do02.imp_z, expr=lm(fn_r_z ~ Reward_bias_20_z + Loss_bias_20_z))))

aim1_table <- DISS_make_table(first_model=mr.rewp_pilt, second_model=mr.fn_pilt)
write.csv(x=aim1_table, file="./tables/RewP_Pilt_table.csv"); aim1_table
```
#### 2.2.1. Separate by block of PILT
```{r}
# summary(pool(with(data=DISS_do02.imp_z, expr=lm(rewp_r_z ~ Reward_bias_20_block1 + Loss_bias_20_block1 + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z))))
# summary(pool(with(data=DISS_do02.imp_z, expr=lm(rewp_r_z ~ Reward_bias_20_block2 + Loss_bias_20_block2 + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z))))

# summary(pool(with(data=DISS_do02.imp_z, expr=lm(fn_r_z ~ Reward_bias_20_block1 + Loss_bias_20_block1 + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z))))
# summary(pool(with(data=DISS_do02.imp_z, expr=lm(fn_r_z ~ Reward_bias_20_block2 + Loss_bias_20_block2 + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z))))
```

## 2.3. Aim 2: Relationship between RewP/FN and Depression/Social Anxiety
```{r}
mr.rewp_sym <- pool(with(data=DISS_do02.imp_z, expr=lm(rewp_r_z ~ S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z)))
summary(pool(with(data=DISS_do02.imp_z, expr=lm(rewp_r_z ~ S5cdic_bdi_perc_z + S5_SIASSPS_z))))

mr.fn_sym <- pool(with(data=DISS_do02.imp_z, expr=lm(fn_r_z ~ S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z)))
summary(pool(with(data=DISS_do02.imp_z, expr=lm(fn_r_z ~ S5cdic_bdi_perc_z + S5_SIASSPS_z))))

aim2_table <- DISS_make_table(first_model=mr.rewp_sym, second_model=mr.fn_sym)
write.csv(x=aim2_table, file="./tables/RewP_Sym_table.csv"); aim2_table
```

## 2.4. Aim 3: Relationship between PILT and Depression/Social Anxiety
```{r}
mr.piltp_sym <- pool(with(data=DISS_do02.imp_z, expr=lm(Reward_bias_20_z ~ S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z)))
summary(pool(with(data=DISS_do02.imp_z, expr=lm(Reward_bias_20_z ~ S5cdic_bdi_perc_z + S5_SIASSPS_z))))

mr.piltn_sym <- pool(with(data=DISS_do02.imp_z, expr=lm(Loss_bias_20_z ~ S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z)))
summary(pool(with(data=DISS_do02.imp_z, expr=lm(Loss_bias_20_z ~ S5cdic_bdi_perc_z + S5_SIASSPS_z))))

aim3_table <- DISS_make_table(first_model=mr.piltp_sym, second_model=mr.piltn_sym)
write.csv(x=aim3_table, file="./tables/PILT_Sym_table.csv"); aim3_table
```
#### 2.4.1. Separate by block of PILT
```{r}
# summary(pool(with(data=DISS_do02.imp_z, expr=lm(Reward_bias_20_block1 ~ S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z))))
# summary(pool(with(data=DISS_do02.imp_z, expr=lm(Reward_bias_20_block2 ~ S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z))))

# summary(pool(with(data=DISS_do02.imp_z, expr=lm(Loss_bias_20_block1 ~ S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z))))
# summary(pool(with(data=DISS_do02.imp_z, expr=lm(Loss_bias_20_block2 ~ S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z))))
```


# 3.0 Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

