---
title: "Analysis script 3: Bayesian analysis of confirmatory analyses"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
These are the primary analyses for Brent Rappaport's doctoral dissertation thesis: "Behavioral, neural, and psychiatric correlates of response to social feedback."

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    options(scipen = 999) #Disable scientific notation
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(brms)       #run Bayes multiple regression analyses
  library(cmdstanr)
  library(bayestestR)
  library(see)
  library(mice)       #multiple imputation
  library(miceadds)   #adding functions to mice
  library(tidyverse)  #plotting/cleaning, etc.
  library(pander)     #make nice tables
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
   Remember to set your seed AFTER you load libraries
```{r}
     set.seed(314)    #Set seed
```

## 1.5. Load data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
      load(file = "../work/data/DISS_do01_nooutliers.RData")       
      DISS_do02_nooutliers <- DISS_do01_nooutliers
      rm("DISS_do01_nooutliers")
      
      load(file = "../work/data/DISS_do01.imp_z.RData")
      DISS_do02.imp_z <- DISS_do01.imp_z
      rm("DISS_do01.imp_z")
```      

# Correlation between RewP and Depression
```{r}
f1 <- 
  brm_multiple(data = DISS_do02.imp_z, 
      family = gaussian,
      rewp_r_z ~ 1 + S5cdic_bdi_perc_z,
      prior = c(prior(normal(0, 1), class = Intercept),
                prior(normal(-0.1, 0.1), class = b),
                prior(normal(0, 1), class = sigma)),
      chains = 4, cores = 4, 
      save_pars=save_pars(all=TRUE),
      sample_prior="yes",
      file="./analysis/corr_brms",
      seed=314)
f1

pooled_r = -0.1
pooled_rse = sqrt((1-(0.1^2))/(757-2))
pooled_r+pooled_rse

# Compute indices for ROPE
pd <- p_direction(f1)
percentage_in_rope <- rope(f1, ci=1, range=c(pooled_r+pooled_rse, -1*pooled_r+pooled_rse))

# plot(pd)
# plot(percentage_in_rope)

# Compute Bayes Factor
f1_un <- unupdate(f1, newdata = DISS_do02.imp_z)
f1_BF <- bayesfactor_parameters(posterior=f1, null = 0, prior = f1_un)
f1_BF$BF[2]
```

## 5.2. Aim 1: Relationship between RewP/FN and PILT-P/N
#### 5.2.1. Multiple regression
```{r}
plan(multicore)
mr.rewp_pilt <- brm_multiple(family = gaussian, 
    rewp_r_z ~ 1 + Reward_bias_20_z + Loss_bias_20_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z,
    prior = c(prior(normal(0,5), class=Intercept),
              prior(normal(0,2), class=b, coef=Reward_bias_20_z),
              prior(normal(0,2), class=b, coef=Loss_bias_20_z),
              prior(normal(0,2), class=b, coef=T20age_z),
              prior(normal(0,2), class=b, coef=sex_f1),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f1),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f2),
              prior(normal(0,2), class=b, coef=PDSIII_Hispanic_f1),
              prior(normal(0,2), class=b, coef=Income_to_Need_z),
              prior(exponential(1), class = sigma)),
    iter=5000, warmup=1000, chains=4, cores=2,
    data=DISS_do02.imp_z,
    file="./analysis/mr.rewp_pilt")
mr.rewp_pilt$rhats
summary(mr.rewp_pilt)

plot(mr.rewp_pilt)
conditional_effects(mr.rewp_pilt)
pp_check(mr.rewp_pilt, nsamples=20)
```

# All other analyses
#### 5.2.4. FN/PILT-Bayes
```{r}
plan(multicore)
mr.fn_pilt <- brm_multiple(family = gaussian, 
    fn_r_z ~ 1 + Reward_bias_20_z + Loss_bias_20_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z,
    prior = c(prior(normal(0,5), class=Intercept),
              prior(normal(0,2), class=b, coef=Reward_bias_20_z),
              prior(normal(0,2), class=b, coef=Loss_bias_20_z),
              prior(normal(0,2), class=b, coef=T20age_z),
              prior(normal(0,2), class=b, coef=sex_f1),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f1),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f2),
              prior(normal(0,2), class=b, coef=PDSIII_Hispanic_f1),
              prior(normal(0,2), class=b, coef=Income_to_Need_z),
              prior(exponential(1), class = sigma)),
    iter=5000, warmup=1000, chains=4, cores=2,
    data=DISS_do02.imp_z,
    file="./analysis/mr.fn_pilt")
mr.fn_pilt$rhats; colMeans(mr.fn_pilt$rhats)
summary(mr.fn_pilt)

plot(mr.fn_pilt)
conditional_effects(mr.fn_pilt)
pp_check(mr.fn_pilt, nsamples=20)
```

## 5.3. Aim 2: Relationship between RewP/FN and Depression/Social Anxiety
#### 5.3.1. Multiple regression
```{r}
mr.rewp_sym <- brm_multiple(family = gaussian, 
    rewp_r_z ~ 1 + S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z,
    prior = c(prior(normal(0,5), class=Intercept),
              prior(normal(-0.1,2), class=b, coef=S5cdic_bdi_perc_z),
              prior(normal(0,2), class=b, coef=S5_SIASSPS_z),
              prior(normal(0,2), class=b, coef=T20age_z),
              prior(normal(0,2), class=b, coef=sex_f2),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f2),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f3),
              prior(normal(0,2), class=b, coef=PDSIII_Hispanic_f2),
              prior(normal(0,2), class=b, coef=Income_to_Need_z),
              prior(exponential(1), class = sigma)),
    iter=5000, warmup=1000, chains=4, cores=2,
    data=DISS_do02.imp_z,
    save_pars=save_pars(all=TRUE),
    sample_prior="yes",
    seed=TRUE,
    backend="cmdstanr",
    file="./analysis/mr.rewp_sym")
summary(mr.rewp_sym)

plot(mr.rewp_sym)
conditional_effects(mr.rewp_sym)
pp_check(mr.rewp_sym, nsamples=20)

# Bayes Factor
## Null model
mr.rewp_sym_null <- brm_multiple(family = gaussian, 
    rewp_r_z ~ 1 + S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z,
    prior = c(prior(normal(0,5), class=Intercept),
              prior(normal(0,2), class=b, coef=S5cdic_bdi_perc_z),
              prior(normal(0,2), class=b, coef=S5_SIASSPS_z),
              prior(normal(0,2), class=b, coef=T20age_z),
              prior(normal(0,2), class=b, coef=sex_f2),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f2),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f3),
              prior(normal(0,2), class=b, coef=PDSIII_Hispanic_f2),
              prior(normal(0,2), class=b, coef=Income_to_Need_z),
              prior(exponential(1), class = sigma)),
    iter=5000, warmup=1000, chains=4, cores=2,
    data=DISS_do02.imp_z,
    save_pars=save_pars(all=TRUE),
    sample_prior="yes",
    seed=314,
    backend="cmdstanr",
    file="./analysis/mr.rewp_sym_null")
summary(mr.rewp_sym_null)

bayes_factor(mr.rewp_sym, mr.rewp_sym_null)
```

```{r}
cor.rewp_sym <- brm_multiple(data = DISS_do02.imp_z, 
      family = gaussian,
      mvbind(rewp_r_z, S5cdic_bdi_perc_z) ~ 1,
      prior = c(prior(normal(0, 100), class = Intercept),
                prior(normal(0, 100), class = sigma, resp = rewp_r_z),
                prior(normal(0, 100), class = sigma, resp = S5cdic_bdi_perc_z),
                prior(lkj(1), class = rescor)),
      iter = 5000, warmup = 1000, chains = 4, cores = 2, 
      seed = 314)

cor.rewp_sym <- brm_multiple(data = DISS_do02.imp_z, 
      family = student,
      mvbind(rewp_r_z, S5cdic_bdi_perc_z) ~ 1,
      prior = c(prior(gamma(2, .1), class = nu),
                prior(normal(0, 100), class = Intercept),
                prior(normal(0, 100), class = sigma, resp = rewp_r_z),
                prior(normal(0, 100), class = sigma, resp = S5cdic_bdi_perc_z),
                prior(lkj(1), class = rescor)),
      iter = 2000, warmup = 500, chains = 4, cores = 2, 
      seed = 314)

cor_test <- stan(file="robust_correlation.stan", data=DISS_do02.imp_z, 
                 iter=2000, warmup=500, chains=4, seed=919)

ggplot(DISS_do02.imp_z, aes(y=rewp_r_z, x=S5cdic_bdi_perc_z)) +
  geom_point()

```

#### 5.3.4 FN/Sym-Bayes
```{r}
mr.fn_sym <- brm_multiple(family = gaussian, 
    fn_r_z ~ 1 + S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z,
    prior = c(prior(normal(0,5), class=Intercept),
              prior(normal(0,2), class=b, coef=S5cdic_bdi_perc_z),
              prior(normal(0,2), class=b, coef=S5_SIASSPS_z),
              prior(normal(0,2), class=b, coef=T20age_z),
              prior(normal(0,2), class=b, coef=sex_f1),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f1),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f2),
              prior(normal(0,2), class=b, coef=PDSIII_Hispanic_f1),
              prior(normal(0,2), class=b, coef=Income_to_Need_z),
              prior(exponential(1), class = sigma)),
    iter=5000, warmup=1000, chains=4, cores=2,
    data=DISS_do02.imp_z,
    file="./analysis/mr.fn_sym")
summary(mr.fn_sym)

plot(mr.fn_sym)
conditional_effects(mr.fn_sym)
pp_check(mr.fn_sym, nsamples=20)
```

## 5.4. Aim 3: Relationship between PILT and Depression/Social Anxiety
#### 5.4.1. Multiple regression
```{r}
mr.piltp_sym <- brm_multiple(family = gaussian, 
    Reward_bias_20_z ~ 1 + S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z,
    prior = c(prior(normal(0,5), class=Intercept),
              prior(normal(0,2), class=b, coef=S5cdic_bdi_perc_z),
              prior(normal(0,2), class=b, coef=S5_SIASSPS_z),
              prior(normal(0,2), class=b, coef=T20age_z),
              prior(normal(0,2), class=b, coef=sex_f1),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f1),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f2),
              prior(normal(0,2), class=b, coef=PDSIII_Hispanic_f1),
              prior(normal(0,2), class=b, coef=Income_to_Need_z),
              prior(exponential(1), class = sigma)),
    iter=2000, warmup=1000, chains=4, cores=2,
    data=DISS_do02.imp_z,
    file="./analysis/mr.piltp_sym")
summary(mr.piltp_sym)

plot(mr.piltp_sym)
conditional_effects(mr.piltp_sym)
pp_check(mr.piltp_sym, nsamples=20)
```

#### 5.4.3. PILTN/Sym-Bayes
```{r}
mr.piltn_sym <- brm_multiple(family = gaussian, 
    Loss_bias_20_z ~ 1 + S5cdic_bdi_perc_z + S5_SIASSPS_z + T20age_z + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need_z,
    prior = c(prior(normal(0,5), class=Intercept),
              prior(normal(0,2), class=b, coef=S5cdic_bdi_perc_z),
              prior(normal(0,2), class=b, coef=S5_SIASSPS_z),
              prior(normal(0,2), class=b, coef=T20age_z),
              prior(normal(0,2), class=b, coef=sex_f1),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f1),
              prior(normal(0,2), class=b, coef=PDSIII_Race_f2),
              prior(normal(0,2), class=b, coef=PDSIII_Hispanic_f1),
              prior(normal(0,2), class=b, coef=Income_to_Need_z),
              prior(exponential(1), class = sigma)),
    iter=2000, warmup=1000, chains=4, cores=2,
    data=DISS_do02.imp_z,
    file="./analysis/mr.piltn_sym")
summary(mr.piltn_sym)

plot(mr.piltn_sym)
conditional_effects(mr.piltn_sym)
pp_check(mr.piltn_sym, nsamples=20)
```

# 3.0 Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```