---
title: "Analysis script 4: Exploratory analyses"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
These are the primary analyses for Brent Rappaport's doctoral dissertation thesis: "Behavioral, neural, and psychiatric correlates of response to social feedback."

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    options(scipen = 999) #Disable scientific notation
    #rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(MASS)       #runs robust linear models
  library(sfsmisc)    #run robust F-test for linear models
  library(MissMech)   #test of MCAR
  library(naniar)     #handle missingness
  library(mice)       #multiple imputation
  library(miceadds)   #adding functions to mice
  library(tidyverse)  #plotting/cleaning, etc.
  library(pander)     #make nice tables
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
   Remember to set your seed AFTER you load libraries
```{r}
     set.seed(919)    #Set seed
```

## 1.5. Load data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
      load(file = "./data/DISS_cleaning07.RData")   
      DISS_do04_full <- DISS_cleaning07  ## first create new data
      rm("DISS_cleaning07")             ## remove old data
```      

## 1.6. Subset data
```{r}
# measures_list <- c("rewp_r","fn_r","p2_r","Reward_bias_20","Loss_bias_20","Reward_bias_20_block1","Reward_bias_20_block2","Loss_bias_20_block1","Loss_bias_20_block2","S5cdic_bdi_perc","S5_SIASSPS","T20age","Income_to_Need")
factors_list <- c("sex","PDSIII_Race","PDSIII_Hispanic","S5psychmed_dos")

for (f in factors_list){ 
    eval(parse(text=paste0("DISS_do04_full$",f,"_f <- with(DISS_do04_full, as.factor(",f,"))"))) 
}

contrasts(DISS_do04_full$sex_f) <- contr.sum(2)
contrasts(DISS_do04_full$PDSIII_Race_f) <- contr.sum(3)
contrasts(DISS_do04_full$PDSIII_Hispanic_f) <- contr.sum(2)
contrasts(DISS_do04_full$S5psychmed_dos_f) <- contr.sum(2)

DISS_do04 <- DISS_do04_full %>% #subset data to only include those that completed Island Getaway task and have T20age
    drop_na(rewp_r, T20age)
```

## 2. Multiple imputation
Conduct multiple imputation using package 'mice' and the following steps outlined here: 
http://dept.stat.lsa.umich.edu/~jerrick/courses/stat701/notes/mi.html
```{r}
# DISS_do01.imp <- mice(DISS_do01[,c(2:5,10:13,18:20)], m = 10, method = 'pmm', seed=919) #generate 10 imputed datasets
# summary(DISS_do01.imp)

# DISS_do01.comp <- complete(DISS_do01.imp, "long", include = TRUE)

# DISS_do01.comp$Reward_bias_20.NA <- cci(DISS_do01$Reward_bias_20)
# DISS_do01.comp$Loss_bias_20.NA <- cci(DISS_do01$Loss_bias_20)
# DISS_do01.comp$S5cdic_bdi_perc.NA <- cci(DISS_do01$S5cdic_bdi_perc)
```

# 3. With P2 component
```{r}
summary(lm(p2_r ~ Reward_bias_20 + Loss_bias_20 + T20age + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need, DISS_do04))
summary(lm(p2_r ~ Reward_bias_20 + Loss_bias_20, DISS_do04))

summary(lm(p2_r ~ S5cdic_bdi_perc + S5_SIASSPS + T20age + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need, DISS_do04))
summary(lm(p2_r ~ S5cdic_bdi_perc + S5_SIASSPS, DISS_do04))
```

# 4. Other measures of MDD
```{r}
#S5MDDCore
summary(lm(rewp_r ~ S5MDDCore, DISS_do04))
summary(lm(fn_r ~ S5MDDCore, DISS_do04))
summary(lm(p2_r ~ S5MDDCore, DISS_do04))

#T20MDDCore
summary(lm(rewp_r ~ T20MDDCore, DISS_do04))
summary(lm(fn_r ~ T20MDDCore, DISS_do04))
summary(lm(p2_r ~ T20MDDCore, DISS_do04))

#S5AvgMDDCore
summary(lm(rewp_r ~ S5AvgMDDCore, DISS_do04))
summary(lm(fn_r ~ S5AvgMDDCore, DISS_do04))
summary(lm(p2_r ~ S5AvgMDDCore, DISS_do04))

#S5AvgMDDCore
summary(lm(rewp_r ~ S5AvgMDDCore, DISS_do04))
summary(lm(fn_r ~ S5AvgMDDCore, DISS_do04))
summary(lm(p2_r ~ S5AvgMDDCore, DISS_do04))

#T20_MDD
summary(lm(rewp_r ~ T20_MDD, DISS_do04))
summary(lm(fn_r ~ T20_MDD, DISS_do04))
summary(lm(p2_r ~ T20_MDD, DISS_do04))

#T20_MDD
summary(lm(rewp_r ~ T20_MDD, DISS_do04))
summary(lm(fn_r ~ T20_MDD, DISS_do04))
summary(lm(p2_r ~ T20_MDD, DISS_do04))

#rel_MDDBP_01
DISS_do04$rel_MDDBP_01 <- ifelse(DISS_do04$rel_MDDBP>=1,1,0)
summary(lm(rewp_r ~ rel_MDDBP_01, DISS_do04))
summary(lm(fn_r ~ rel_MDDBP_01, DISS_do04))
summary(lm(p2_r ~ rel_MDDBP_01, DISS_do04))
```

# 5. Other measures of Social phobia
```{r}
#T20_SOC
summary(lm(rewp_r ~ T20_SOC, DISS_do04))
summary(lm(fn_r ~ T20_SOC, DISS_do04))
summary(lm(p2_r ~ T20_SOC, DISS_do04))

#S5SOC
summary(lm(rewp_r ~ S5SOC, DISS_do04))
summary(lm(fn_r ~ S5SOC, DISS_do04))
summary(lm(p2_r ~ S5SOC, DISS_do04))
```

# 6. Voting behavior
```{r}
summary(lm(Keep_prop ~ S5cdic_bdi_perc, DISS_do04))
summary(lm(Keep_prop ~ S5_SIASSPS, DISS_do04))

summary(lm(Keep_prop ~ Reward_bias_20, DISS_do04))
summary(lm(Keep_prop ~ Loss_bias_20, DISS_do04))

#Extension of Frontiers paper )with peer victimization)
summary(lm(Keep_prop ~ PPr_Avg_early + T20age, DISS_do04))
summary(lm(Keep_prop ~ T18hbqhPRr + T20age, DISS_do04))

summary(lm(rewp275375_r ~ PPr_Avg_early, DISS_do04))
summary(lm(rewp275375_r ~ T18hbqhPRr, DISS_do04))

ggplot(DISS_do04, aes(x=PPr_Avg_early, y=Keep_prop)) +
  geom_point() +
  stat_smooth(method="lm")
```

# 7. Post-task questionnaire
```{r}
summary(lm(rewp_r ~ belonging, DISS_do04))
summary(lm(fn_r ~ belonging, DISS_do04))
summary(lm(p2_r ~ belonging, DISS_do04))

summary(lm(rewp_r ~ control, DISS_do04))
summary(lm(fn_r ~ control, DISS_do04))
summary(lm(p2_r ~ control, DISS_do04))

summary(lm(rewp_r ~ meaningful_existence, DISS_do04))
summary(lm(fn_r ~ meaningful_existence, DISS_do04))
summary(lm(p2_r ~ meaningful_existence, DISS_do04))

summary(lm(rewp_r ~ task_disengagement, DISS_do04))
summary(lm(fn_r ~ task_disengagement, DISS_do04))
summary(lm(p2_r ~ task_disengagement, DISS_do04))

summary(lm(rewp_r ~ preoccupation_with_exclusion, DISS_do04)) #*
summary(lm(fn_r ~ preoccupation_with_exclusion, DISS_do04))
summary(lm(p2_r ~ preoccupation_with_exclusion, DISS_do04))

summary(lm(rewp_r ~ self_esteem, DISS_do04))
summary(lm(fn_r ~ self_esteem, DISS_do04))
summary(lm(p2_r ~ self_esteem, DISS_do04))

summary(lm(rewp_r ~ survivor, DISS_do04))
summary(lm(fn_r ~ survivor, DISS_do04))
summary(lm(p2_r ~ survivor, DISS_do04))
```

# 8. Income to needs
```{r}
summary(lm(rewp_r ~ Income_to_Need, DISS_do04)) #*
summary(lm(fn_r ~ Income_to_Need, DISS_do04))
summary(lm(p2_r ~ Income_to_Need, DISS_do04)) #*

ggplot(DISS_do04, aes(x=Income_to_Need, y=rewp_r)) +
  geom_point() +
  stat_smooth(formula=y~x, method="lm")

ggplot(DISS_do04, aes(x=Income_to_Need, y=fn_r)) +
  geom_point() +
  stat_smooth(formula=y~x, method="lm")

ggplot(DISS_do04, aes(x=Income_to_Need, y=p2_r)) +
  geom_point() +
  stat_smooth(formula=y~x, method="lm")
```

# 9. Raw components scores
```{r}
summary(lm(rewp_ACC ~ Reward_bias_20 + Loss_bias_20 + T20age + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need, DISS_do04))
summary(lm(rewp_ACC ~ Reward_bias_20 + Loss_bias_20, DISS_do04))

summary(lm(rewp_REJ ~ Reward_bias_20 + Loss_bias_20 + T20age + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need, DISS_do04))
summary(lm(rewp_REJ ~ Reward_bias_20 + Loss_bias_20, DISS_do04))

summary(lm(rewp_ACC ~ S5cdic_bdi_perc + S5_SIASSPS + T20age + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need, DISS_do04))
summary(lm(rewp_ACC ~ S5cdic_bdi_perc + S5_SIASSPS, DISS_do04))

summary(lm(rewp_REJ ~ S5cdic_bdi_perc + S5_SIASSPS + T20age + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need, DISS_do04))
summary(lm(rewp_REJ ~ S5cdic_bdi_perc + S5_SIASSPS, DISS_do04))
```



# . Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

