---
title: "Analysis script 4: Exploratory analyses"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
These are the primary analyses for Brent Rappaport's doctoral dissertation thesis: "Behavioral, neural, and psychiatric correlates of response to social feedback."

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    options(scipen = 999) #Disable scientific notation
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(MASS)       #runs robust linear models
  library(sfsmisc)    #run robust F-test for linear models
  library(MissMech)   #test of MCAR
  library(naniar)     #handle missingness
  library(mice)       #multiple imputation
  library(miceadds)   #adding functions to mice
  library(tidyverse)  #plotting/cleaning, etc.
  library(pander)     #make nice tables
  library(lavaan)     #SEM analyses
  library(beepr)      #beep upon completion
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
   Remember to set your seed AFTER you load libraries
```{r}
     set.seed(314)    #Set seed
```

## 1.5. Load data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
      load(file = "../work/data/DISS_do01_full.RData")   
      DISS_do04_full_nooutliers <- DISS_do01_full_nooutliers
      rm("DISS_do01_full_nooutliers")

      load(file = "../work/data/DISS_do01_nooutliers.RData")       
      DISS_do04_nooutliers <- DISS_do01_nooutliers
      rm("DISS_do01_nooutliers")
      
      load(file = "../work/data/DISS_do01.RData")   
      DISS_do04 <- DISS_do01
      rm("DISS_do01")
      
      load(file = "../work/data/DISS_do01.imp.RData")
      DISS_do04.imp <- DISS_do01.imp
      rm("DISS_do01.imp")
      
      load(file = "../work/data/DISS_do01.imp_z.RData")
      DISS_do04.imp_z <- DISS_do01.imp_z
      rm("DISS_do01.imp_z")
      
      load(file = "./data/DISS_cleaning07.RData")
      DISS_do04_full <- DISS_cleaning07  ## first create new data
      rm("DISS_cleaning07")             ## remove old data
      
      load(file = "./data/DISS_cleaning04_hbq.RData")   
      DISS_do04_hbq <- DISS_cleaning04_hbq  ## first create new data
      rm("DISS_cleaning04_hbq")             ## remove old data
      
      CRUNCH <- expss::read_spss("../../CRUNCH/PDS_III_S5_crunched_10_23_20.sav")
      crunch <- CRUNCH; rm(CRUNCH)
      
      DISS_do04_exp <- Reduce(function(x,y) merge(x,y,by="Subid",all=TRUE),list(DISS_do04_full, DISS_do04_hbq, crunch))
```      

# 2. Check the PILT is calculated similarly to past waves
```{r}
# Check the PILT P and PILT N
sum(!is.na(DISS_do04_exp$S5Block1_Bias_FP))
sum(!is.na(DISS_do04_exp$Reward_bias_20_block1))

# PILT P
corr.test(DISS_do04_exp$S5Block1_Bias_FP, DISS_do04_exp$Reward_bias_20_block1, method="pearson", use="complete.obs")
corr.test(DISS_do04_exp$S5Block2_Bias_FP, DISS_do04_exp$Reward_bias_20_block2, method="pearson", use="complete.obs")
# PILT N
corr.test(DISS_do04_exp$S5Block1_Bias_FN, DISS_do04_exp$Loss_bias_20_block1, method="pearson", use="complete.obs")
corr.test(DISS_do04_exp$S5Block2_Bias_FN, DISS_do04_exp$Loss_bias_20_block2, method="pearson", use="complete.obs")
```

# 4. Other measures of MDD
```{r}
DISS_do04$rel_MDDBP_01 <- ifelse(DISS_do04$rel_MDDBP>=1,1,0)

for (m in c("T20MDDCore","S5AvgMDDCore","T20_MDD","T1MDDCore","rel_MDDBP_01")){
  for (e in c("rewp_r","fn_r","p2_r","n1_r")){
    print(paste0("##############################",m,"##############################"))
    print(paste0("##############################",e,"##############################"))
      print(eval(parse(text=paste0("summary(lm(",e,"~",m,", DISS_do04))"))))
  }}
```

## 4.1 Growth models
```{r}
MDDCORE.growth <- '
#Define latent variables
PILT.P =~ 1*Reward_bias_20
PILT.N =~ 1*Loss_bias_20
# REWP =~ 1*rewp_r
# FN =~ 1*fn_r
MDD =~ 1*T20MDDCore.x
# SAD =~ 1*S5_SIASSPS

#Define slope
# sMDD =~ 0*T1MDDCore.x	+ 1.0351*T3MDDCore.x + 2.0029*T5MDDCore.x + 4.5900*T6MDDCore.x + 5.7196*T8MDDCore.x + 6.7056*T10MDDCore.x + 7.7505*T12MDDCore.x + 8.7730*T14MDDCore.x + 11.8208*T18MDDCore.x
sMDD =~ 0*T1MDDCore.x	+ 1*T3MDDCore.x + 2*T5MDDCore.x + 4.5*T6MDDCore.x + 5.5*T8MDDCore.x + 6.5*T10MDDCore.x + 7.5*T12MDDCore.x + 8.5*T14MDDCore.x + 11.5*T18MDDCore.x

#Define intercept
iMDD =~ 1*T1MDDCore.x	+ 1*T3MDDCore.x + 1*T5MDDCore.x + 1*T6MDDCore.x + 1*T8MDDCore.x + 1*T10MDDCore.x + 1*T12MDDCore.x + 1*T14MDDCore.x + 1*T18MDDCore.x

#Regressions
# iMDD ~ REWP + FN
# sMDD ~ REWP + FN
iMDD ~ PILT.P + PILT.N
sMDD ~ PILT.P + PILT.N
iMDD ~ MDD
sMDD ~ MDD

iMDD ~ sex.x + T20age.x + Income_to_Need
sMDD ~ sex.x + T20age.x + Income_to_Need
'
fit.MDDCORE.growth <- growth(MDDCORE.growth, data=DISS_do04_exp, missing="FIML", estimator="MLR")
# beep(sound = 1, expr = NULL)

summary(fit.MDDCORE.growth, fit.measures=T, standardized=T)
```

## 4.2 Growth models (vicitmization)
```{r}
data_hbq <- read.csv("../../CRUNCH/-HBQ/HBQ_dataset.csv")
DISS_do04_exp_hbq <- merge(DISS_do04_exp, data_hbq, by="Subid")

DISS_do04_exp_hbq$T6hbqPR <- DISS_do04_exp_hbq$T6hbqhPR
DISS_do04_exp_hbq$T6hbqPR[!is.na(DISS_do04_exp_hbq$T6hbqpPR)] <- DISS_do04_exp_hbq$T6hbqpPR[!is.na(DISS_do04_exp_hbq$T6hbqpPR)] 

DISS_do04_exp_hbq$T8hbqPR <- DISS_do04_exp_hbq$T8hbqhPR
DISS_do04_exp_hbq$T8hbqPR[!is.na(DISS_do04_exp_hbq$T8hbqpPR)] <- DISS_do04_exp_hbq$T8hbqpPR[!is.na(DISS_do04_exp_hbq$T8hbqpPR)] 
```

```{r}
HBQ.growth <- '
#Define latent variables
PILT.P =~ 1*Reward_bias_20
PILT.N =~ 1*Loss_bias_20
REWP =~ 1*rewp_r
FN =~ 1*fn_r
MDD =~ 1*S5cdic_bdi_perc
SAD =~ 1*S5_SIASSPS

#Define slope
sVIC =~ 0*T1hbqpPR.x	+ 1.0351*T3hbqpPR.x + 2.0029*T5hbqpPR.x + 4.5900*T6hbqPR + 5.7196*T8hbqPR + 6.7056*T10hbqhPR + 7.7505*T12hbqhPR + 8.7730*T14hbqhPR + 11.8208*T18hbqhPR.x

#Define intercept
iVIC =~ 1*T1hbqpPR.x	+ 1*T3hbqpPR.x + 1*T5hbqpPR.x + 1*T6hbqPR + 1*T8hbqPR + 1*T10hbqhPR + 1*T12hbqhPR + 1*T14hbqhPR + 1*T18hbqhPR.x

#Regressions
iVIC ~ REWP + FN
sVIC ~ REWP + FN
iVIC ~ PILT.P + PILT.N
sVIC ~ PILT.P + PILT.N
iVIC ~ MDD + SAD
sVIC ~ MDD + SAD
'

fit.HBQ.growth <- growth(HBQ.growth, data=DISS_do04_exp_hbq, missing="FIML", estimator="MLR")

summary(fit.HBQ.growth, fit.measures=T, standardized=T)

DISS_do04_exp_hbq$mean_vic <- rowMeans(DISS_do04_exp_hbq[,c("T1hbqpPR.x","T3hbqpPR.x","T5hbqpPR.x","T6hbqPR","T8hbqPR","T10hbqhPR","T12hbqhPR","T14hbqhPR","T18hbqhPR.x")], na.rm=TRUE)/rowSums(!is.na(DISS_do04_exp_hbq[,c("T1hbqpPR.x","T3hbqpPR.x","T5hbqpPR.x","T6hbqPR","T8hbqPR","T10hbqhPR","T12hbqhPR","T14hbqhPR","T18hbqhPR.x")]))

summary(lm(rewp_r ~ mean_vic, DISS_do04_exp_hbq))
summary(lm(fn_r ~ mean_vic, DISS_do04_exp_hbq))
summary(lm(p2_r ~ mean_vic, DISS_do04_exp_hbq))
summary(lm(n1_r ~ mean_vic, DISS_do04_exp_hbq))

summary(lm(Keep_prop ~ mean_vic, DISS_do04_exp_hbq))
summary(lm(Reward_bias_20 ~ mean_vic, DISS_do04_exp_hbq))
summary(lm(S5cdic_bdi_perc ~ mean_vic, DISS_do04_exp_hbq)) #*
summary(lm(S5_SIASSPS ~ mean_vic, DISS_do04_exp_hbq))
```

# 5. Other measures of Social phobia
```{r}
#T20_SOC
summary(lm(rewp_r ~ T20_SOC, DISS_do04))
summary(lm(fn_r ~ T20_SOC, DISS_do04))
summary(lm(p2_r ~ T20_SOC, DISS_do04))
summary(lm(n1_r ~ T20_SOC, DISS_do04))
```

# 5. BPD
```{r}
for (m in c("S4BPFSC_NR","S4BPFSC_T","S5BPFSC_NR","S5BPFSC_T","S5BPFSC_SH")){
  for (e in c("rewp_r","fn_r","p2_r","n1_r")){
    print(paste0("##############################",m,"##############################"))
    print(paste0("##############################",e,"##############################"))
      print(eval(parse(text=paste0("summary(lm(",e,"~",m,", DISS_do04_exp))"))))
  }}
```

# 6. Voting behavior
```{r}
summary(lm(Keep_prop ~ S5cdic_bdi_perc, DISS_do04))
summary(lm(Keep_prop ~ S5_SIASSPS, DISS_do04))

summary(lm(Keep_prop ~ Reward_bias_20, DISS_do04))
summary(lm(Keep_prop ~ Loss_bias_20, DISS_do04))

summary(lm(Keep_prop ~ rewp_r, DISS_do04))
summary(lm(Keep_prop ~ fn_r, DISS_do04))
summary(lm(Keep_prop ~ p2_r, DISS_do04))
summary(lm(Keep_prop ~ n1_r, DISS_do04))

summary(lm(Keep_prop ~ Income_to_Need, DISS_do04))

## Peer relations
summary(lm(Keep_prop~T18hbqhPS, DISS_do04))
```

#7. Extension of Frontiers paper with peer victimization)
```{r}
summary(lm(Keep_prop ~ PPr_Avg_early + T20age, DISS_do04))
summary(lm(Keep_prop ~ T18hbqhPRr + T20age, DISS_do04))

summary(lm(rewp275375_r ~ PPr_Avg_early, DISS_do04))
summary(lm(rewp275375_r ~ T18hbqhPRr, DISS_do04))

ggplot(DISS_do04, aes(x=PPr_Avg_early, y=Keep_prop)) +
  geom_point() +
  stat_smooth(method="lm")
```

# 7. Post-task questionnaire
```{r}
for (m in c("belonging","control","meaningful_existence","task_disengagement","preoccupation_with_exclusion","self_esteem","survivor")){
  for (e in c("rewp_r","fn_r","p2_r","n1_r")){
    print(paste0("##############################",m,"##############################"))
    print(paste0("##############################",e,"##############################"))
      print(eval(parse(text=paste0("summary(lm(",e,"~",m,", DISS_do04_exp))"))))
  }}
```
Preoccupation with exclusion negatively related to RewP

# 8. Income to needs
```{r}
summary(lm(rewp_r ~ Income_to_Need, DISS_do04)) #*
summary(lm(fn_r ~ Income_to_Need, DISS_do04))
summary(lm(p2_r ~ Income_to_Need, DISS_do04)) #*

rewp_i2n <- lm(rewp_r ~ Income_to_Need + S5cdic_bdi_perc + S5_SIASSPS + T20age.x + sex.x + PDSIII_Race.x + PDSIII_Hispanic.x, DISS_do04_exp) #* #fdr*
fn_i2n <- lm(fn_r ~ Income_to_Need + S5cdic_bdi_perc + S5_SIASSPS + T20age.x + sex.x + PDSIII_Race.x + PDSIII_Hispanic.x, DISS_do04_exp)
p2_i2n <- lm(p2_r ~ Income_to_Need + S5cdic_bdi_perc + S5_SIASSPS + T20age.x + sex.x + PDSIII_Race.x + PDSIII_Hispanic.x, DISS_do04_exp) #*

summary(lm(rewp_ACC ~ Income_to_Need, DISS_do04)) #*
summary(lm(rewp_REJ ~ Income_to_Need, DISS_do04))

summary(lm(Reward_bias_20 ~ Income_to_Need, DISS_do04))
summary(lm(Loss_bias_20 ~ Income_to_Need, DISS_do04)) #**

summary(lm(Income_to_Need ~ rewp_r + Loss_bias_20, DISS_do04)) #**

p.adjust(p=c(tidy(rewp_i2n)$p.value[2], tidy(fn_i2n)$p.value[2], tidy(fn_i2n)$p.value[2]), method="fdr")

ggplot(DISS_do04, aes(x=Income_to_Need, y=rewp_r)) +
  geom_point() +
  stat_smooth(formula=y~x, method="lm")

ggplot(DISS_do04, aes(x=Income_to_Need, y=Loss_bias_20)) +
  geom_point() +
  stat_smooth(formula=y~x, method="lm")
```


# 9. Life events
```{r}
for (m in c("LEA_S5_N","LEA_S4toS5_N","LEB_S5_N","LEB_S4toS5_N","LEB_N_PS",
            "LE_romance_S5 + LE_otherrel_S5","LEB_S5_N*S5Income_to_Need","LEB_S5_N*Income_to_Need","LEB_S5_N*S5AvgMDDCore.x","LEB_S4toS5_N*S5MDDCore.x")){
  for (e in c("rewp_r","fn_r","p2_r","n1_r")){
    print(paste0("##############################",m,"##############################"))
    print(paste0("##############################",e,"##############################"))
      print(eval(parse(text=paste0("summary(lm(",e,"~",m,", DISS_do04_exp))"))))
  }}


# Traumatic life events
summary(lm(fn_r ~ LEB_S5_N, DISS_do04_exp)) #*
summary(lm(n1_r ~ LEB_S5_N, DISS_do04_exp)) #*

summary(lm(rewp_r ~ LEB_S4toS5_N, DISS_do04_exp))
summary(lm(fn_r ~ LEB_S4toS5_N, DISS_do04_exp))
summary(lm(p2_r ~ LEB_S4toS5_N, DISS_do04_exp)) #*
summary(lm(n1_r ~ LEB_S4toS5_N, DISS_do04_exp)) #**

# Relationship life events
summary(lm(fn_r ~ LE_romance_S5 + LE_otherrel_S5, data = DISS_do04_exp)) #*
summary(lm(n1_r ~ LE_romance_S5 + LE_otherrel_S5, data = DISS_do04_exp)) #*

# Preschool traumatic life events
summary(lm(rewp_r ~ LEB_N_PS, DISS_do04_exp)) #* (wrong direction)
```

# 10. Bis/Bas
```{r}
S5bis_bas <- c("S5BAS_C_drive","S5BAS_C_funseek","S5BAS_C_funseek2","S5BAS_C_reward","S5BAS_C_reward2","S5BIS_C","S5BIS_C2","S5BAS_C_reward_revised","S5BAS_C_reward_revised2","S5BIS_C_revised")

for(c in c("rewp_r","fn_r","p2_r","n1_r")) {
  for (m in S5bis_bas){
    print(paste0("###################### COMPONENT: ",c," ######################"))
    print(paste0("###################### SYMPTOM MEASURE: ",m," ######################"))
    print(eval(parse(text=paste0("summary(lm(",c," ~ ",m,", data=DISS_do04_exp))[4]"))))
  }
}

summary(lm(fn_r~S5BIS_C, DISS_do04_exp)) #*
summary(lm(fn_r~S5BIS_C2, DISS_do04_exp)) #*

ggplot(DISS_do04_exp, aes(y=fn_r, x=S5BIS_C2)) +
  geom_point() +
  stat_smooth(method=lm)
```

# 11. Raw components scores
```{r}
summary(lm(rewp_ACC ~ Reward_bias_20 + Loss_bias_20 + T20age + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need, DISS_do04))
summary(lm(rewp_ACC ~ Reward_bias_20 + Loss_bias_20, DISS_do04))

summary(lm(rewp_REJ ~ Reward_bias_20 + Loss_bias_20 + T20age + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need, DISS_do04))
summary(lm(rewp_REJ ~ Reward_bias_20 + Loss_bias_20, DISS_do04))

summary(lm(rewp_ACC ~ S5cdic_bdi_perc + S5_SIASSPS + T20age + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need, DISS_do04))
summary(lm(rewp_ACC ~ S5cdic_bdi_perc + S5_SIASSPS, DISS_do04))

summary(lm(rewp_REJ ~ S5cdic_bdi_perc + S5_SIASSPS + T20age + sex_f + PDSIII_Race_f + PDSIII_Hispanic_f + Income_to_Need, DISS_do04))
summary(lm(rewp_REJ ~ S5cdic_bdi_perc + S5_SIASSPS, DISS_do04))
```


# 12. Analyses for Katherine
```{r}
crunch_new <- expss::read_spss("../../CRUNCH/PDS_III_S5_crunched_01_27_21.sav")
DISS_do04_new <- merge(DISS_do04_full, crunch_new, by="Subid")

summary(lm(rewp_r~T14hbqhPS, DISS_do04_new))
summary(lm(rewp_r~T18hbqhPS, DISS_do04_new))

summary(lm(rewp_r~S3hbqhPS, DISS_do04_new))
summary(lm(rewp275375_r~S3hbqhPS + sex.x + negval_Z_AD + Income_to_Need_PS, DISS_do04_new))

summary(lm(rewp_r~anhed_Z_AD + sex.x + negval_Z_AD + Income_to_Need_PS, DISS_do04_new))
summary(lm(rewp_r~BPFSC_total_16up + sex.x + negval_Z_AD + Income_to_Need_PS, DISS_do04_new))

summary(lm(BPFSC_total_16up~S3hbqhPS + sex.x + negval_Z_AD + Income_to_Need_PS, DISS_do04_new))
```
Prosocial related more to RewP to IG than Doors?

# 13. Observational coding
```{r}
for (m in c("T135meanEMO","T135meanAGR")){
  for (e in c("rewp_r","fn_r")){
    print(paste0("##############################",m,"##############################"))
    print(paste0("##############################",e,"##############################"))
      print(eval(parse(text=paste0("summary(lm(",e,"~",m,", DISS_do04_exp))"))))
  }}

summary(lm(fn_r ~ T135meanEMO, DISS_do04_exp))
summary(lm(fn_r ~ T135meanEMO + T20age.x + sex.x + Income_to_Need, DISS_do04_exp))
summary(lm(fn_r ~ T135meanEMO + T20age.x + sex.x + PDSIII_Race.x + PDSIII_Hispanic.x + Income_to_Need, DISS_do04_exp))
summary(lm(fn_r ~ T135meanEMO + S5cdic_bdi_perc + S5_SIASSPS + T20age.x + sex.x + PDSIII_Race.x + PDSIII_Hispanic.x + Income_to_Need, DISS_do04_exp))

for (m in c("S5cope_OC_C","S5cope_UC_C","S5cope_OC_P","S5cope_UC_P")){
  for (e in c("rewp_r","fn_r","p2_r","n1_r")){
    print(paste0("##############################",m,"##############################"))
    print(paste0("##############################",e,"##############################"))
      print(eval(parse(text=paste0("summary(lm(",e,"~",m,", DISS_do04_exp))"))))
  }}
```
N=101
FN & Neuroticism (positively associated)
FN & Curiosity (negatively associated)


# . Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

