---
title: "Follow-up analyses to Rappaport et al., 2019 from Frontiers"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
These are follow-up analsyes to the Rappaport et al., 2019 manuscript that investigated relationships between peer victimization and response to social and monetary rewards/losses in a subset of the total sample. These analyses represent the same analyses for the social task (Island Getaway) but with the entire full sample.

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    #rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  getwd()
  here()
```

## 1.4. Set seed
   Remember to set your seed AFTER you load libraries
```{r}
     set.seed(8675309)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
      load(file = "./data/wf_cleaning01.RData")   
      wf_cleaning02 <- wf_cleaning01  ## first create new data
      rm("wf_cleaning01")             ## remove old data
```

# 2. Regressions
## 2.1. Voting behavior during IG & Peer Victimization
```{r}
#Early peer victimization  
summary(rlm(Keep_prop ~ PPr_Avg_early, DISS_do01))[4]; 
round(f.robftest(rlm(Keep_prop ~ PPr_Avg_early, DISS_do01), var = "PPr_Avg_early")$p.value,3); 
round(confint.default(rlm(Keep_prop ~ PPr_Avg_early, DISS_do01))[2,],3)

ggplot(DISS_do01, aes(x=PPr_Avg_early, y=Keep_prop)) +
  geom_point() +
  geom_smooth(method = lm, se = TRUE)

  ## With age, sex, race covariates
  summary(rlm(Keep_prop ~ PPr_Avg_early + sex + T20age + PDSIII_Race, DISS_do01))[4]; 
  round(f.robftest(rlm(Keep_prop ~ PPr_Avg_early + sex + T20age + PDSIII_Race, DISS_do01), var = "PPr_Avg_early")$p.value,3); 
  round(confint.default(rlm(Keep_prop ~ PPr_Avg_early + sex + T20age + PDSIII_Race, DISS_do01))[2,],3)
  
#Recent peer victimization  
summary(rlm(Keep_prop ~ T18hbqhPRr, DISS_do01))[4]; 
round(f.robftest(rlm(Keep_prop ~ T18hbqhPRr, DISS_do01), var = "T18hbqhPRr")$p.value,3); 
round(confint.default(rlm(Keep_prop ~ T18hbqhPRr, DISS_do01))[2,],3)

  ## With covariates
  summary(rlm(Keep_prop ~ T18hbqhPRr + sex + T20age + PDSIII_Race, DISS_do01))[4]; 
  round(f.robftest(rlm(Keep_prop ~ T18hbqhPRr + sex + T20age + PDSIII_Race, DISS_do01), var = "T18hbqhPRr")$p.value,3); 
  round(confint.default(rlm(Keep_prop ~ T18hbqhPRr + sex + T20age + PDSIII_Race, DISS_do01))[2,],3)
  
ggplot(DISS_do01, aes(x=T18hbqhPRr, y=Keep_prop)) +
  geom_point() +
  geom_smooth(method = lm, se = TRUE)
```

# 2 Save Data
```{r}
save(object, file="./data/FILENAME.RData")
```

# 3 Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

